---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTbuMxGp-qjiN31z4rOl4_1bCwOk4R22lZgqhDt1vuY7TFe44S-2EdEzfdlPe4PvSfgSS3Qi5aoyMCy/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    minutes = `How many minutes did you spend on TikTok?`,
    content = `What type of content did you mostly watch?`,
    location = `Where were you when using TikTok?`,
    time_of_day = `What time of day was it?`,
    reason = `Why did you open TikTok this time?`
  )
```

## TikTok usage patterns

This report shows patterns in my TikTok use based on the data I collected.

I recorded `r nrow(latest_data)` observations in total.

The average time spent on TikTok was `r round(mean(latest_data$minutes, na.rm = TRUE), 1)` minutes.

The longest TikTok session was `r max(latest_data$minutes, na.rm = TRUE)` minutes, and the shortest was `r min(latest_data$minutes, na.rm = TRUE)` minutes.

### Most watched TikTok content

```{r}
ggplot(latest_data, aes(x = content)) +
  geom_bar() +
  labs(
    title = "Most watched TikTok content",
    x = "Content type",
    y = "Count"
  )
```

### Where TikTok was used

```{r}
ggplot(latest_data, aes(x = location)) +
  geom_bar() +
  labs(
    title = "Where TikTok was used",
    x = "Location",
    y = "Count"
  )
```

### Time of day TikTok was used

```{r}
ggplot(latest_data, aes(x = time_of_day)) +
  geom_bar() +
  labs(
    title = "Time of day TikTok was used",
    x = "Time of day",
    y = "Count"
  )
```

### Why TikTok was opened

```{r}
ggplot(latest_data, aes(x = reason)) +
  geom_bar() +
  labs(
    title = "Reasons for opening TikTok",
    x = "Reason",
    y = "Count"
  )
```