---
title: "Project 4"
author: "Hongyi Zhu"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```
## Introduction

This project investigates my TikTok usage habits over time. 
I collected data about how long I spent on TikTok, what type of content I watched, what time of day I used TikTok, and why I opened the app.

The data was collected using a Google Form. 
I continued using the same form from Project 2 because the questions were already useful for tracking my TikTok habits.

Only I collected the data for this project. 
I recorded around 50 observations over multiple days.

I focused on variables such as content type and time of day because I wanted to understand my TikTok behaviour patterns.

I used bar charts because they clearly compare categories. 
I also used a line graph to show how TikTok activity changed throughout the day.

At first, I had some problems with timestamps and plotting the hourly data, but I fixed the issue by converting the time format correctly.

## Visual data story

[Click here to view my visual data story](https://patrickzzhy.github.io/stats220/visual_data_story.html)

I believe my visual data story demonstrates creativity because I used multiple visualisations and organised the story using progressive sections. 
The visualisations help explain patterns in my TikTok usage clearly and simply.

## Learning reflection

One important thing I learned from Module 4 was how visualisations can communicate information more effectively than raw numbers.

I also learned how to use ggplot2 to create different chart types and customise graphs using titles, labels, and themes.

In the future, I would like to learn more about interactive visualisations and dashboard design because they can make data stories more engaging.

## Appendix

```{r}
library(tidyverse)
library(lubridate)

logged_data <- read_csv("tiktok_usage.csv")


content_summary <- logged_data %>%
  count(`What type of content did you mostly watch?`)

content_plot <- ggplot(
  content_summary,
  aes(
    x = `What type of content did you mostly watch?`,
    y = n
  )
) +
  geom_col(fill = "skyblue") +
  labs(
    title = "Most Watched TikTok Content",
    x = "Content Type",
    y = "Count"
  ) +
  theme_minimal()



ggsave("content_plot.png")

duration_summary <- logged_data %>%
  group_by(`What time of day was it?`) %>%
  summarise(
    avg_duration =
      mean(`How many minutes did you spend on TikTok?`)
  )

duration_plot <- ggplot(
  duration_summary,
  aes(
    x = `What time of day was it?`,
    y = avg_duration
  )
) +
  geom_col(fill = "orange") +
  labs(
    title = "Average TikTok Usage by Time of Day",
    x = "Time of Day",
    y = "Average Minutes"
  ) +
  theme_minimal()



ggsave("duration_plot.png")

logged_data <- read_csv("tiktok_usage.csv")

logged_data <- logged_data %>%
  mutate(
    Timestamp = parse_date_time(
      Timestamp,
      orders = c(
        "mdy HMS",
        "mdy HM",
        "dmy HMS",
        "dmy HM",
        "ymd HMS",
        "ymd HM"
      )
    ),
    hour = hour(Timestamp)
  )

hour_summary <- logged_data %>%
  filter(!is.na(hour)) %>%
  group_by(hour) %>%
  summarise(
    count = n()
  )

hour_plot <- ggplot(
  hour_summary,
  aes(x = hour, y = count)
) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs(
    title = "TikTok Usage Throughout the Day",
    x = "Hour of Day",
    y = "Number of Sessions"
  ) +
  theme_minimal()



ggsave("hour_plot.png")
```
